% vim:set et fenc=utf-8 ft=tex sw=2 ts=2 tw=72:

\newif\ifdraft
% \drafttrue

\ifdraft
        \documentclass[draft]{IEEEtran}
        \def\baselinestretch{1}
        % \setlength{\marginparwidth}{1.5cm}
\else
        \documentclass[conference]{IEEEtran}
\fi

\input{preamble.tex}

\begin{document}

\title{\TheTitle}

\author{
        \IEEEauthorblockA{\TheAuthors}
        \IEEEauthorblockN{Department of Computer Science,
                University of Victoria, Canada.}
        \IEEEauthorblockA{Email: \TheEmails}
}
\maketitle

\begin{abstract}

  \input{abstract.tex}

\end{abstract}


\begin{IEEEkeywords}
  \TheKeywords
\end{IEEEkeywords}

\input{introduction.tex}

\label{sec:background}

\input{background.tex}


\input{model.tex}

\section{Visualizing the \mt of Linux}

The goal of \tool is to simplify the navigation of the kernel commit
information, specifically focusing on merges. This is done by leveraging
the \mt to inspect how commits are merged on the path to the
master branch of the repository.

\subsection{Use cases}

We designed \tool with two use-cases in mind, though a user may switch
between the cases as they work.

\noindent \textbf{Use-case 1: top-to-bottom approach}
\label{sec:usecase1}\\ These are users that are maintaining a section of
the kernel and would like to pick a merge (including all commits that it
merges) and merge it directly into their current repository. This is
useful for reducing the amount of re-implementation work necessary for
integration. For these users, it is important to have the ability to
aggregate metadata about files and modules being effected by the merge.
Also, it is important for these users to be able to navigate from the
root of the \mt toward the leaves.

\noindent \textbf{Use-case 2: bottom-to-top approach}
\label{sec:usecase2}\\ These are users that start with a known merge or
commit and would like to see what other changes are being made in
commits that are in the same merge, including knowing the \mt
they belong to. This is useful to see what other commits are related to
the current commit and how they get joined into merges that eventually
end in the master branch. This is primarily for maintainers that need to
perform some specific cherry picking of commits. We must provide these
users a mechanism for navigating from a single commit toward the master
branch, allowing them to see other commits that might be related to
their original commit.

\subsection{Data Model}

In our visualizations, we leverage the \mt model described in
Section~\ref{sec:mergetree}. In this model, commits are either on the
master branch, or part of a tree which is rooted at a merge into the
master branch. Each commit, whether a merge or non-merge, has only one
parent, with the exception of the root which has no parents. Non-merge
commits contain the metadata for the changes made. This metadata
includes the files changed, the lines added and removed from each file,
the author, the date the commit was merged into the merge that led to
being merged into the kernel, the date the commit was authored, the
patch, and the commit log. Merges contain similar metadata, the author
of the merge, the committer of the merge, if it has been rebased, the
log, the commit date, and the author date, and potentially, changes
necessary to address conflicts during the merge.

\section{Design and Implementation}

\input{design.tex}

\input{relatedwork.tex}

\input{study.tex}

\input{discussion.tex}

\input{conclusion.tex}

\balance

% \nocite{*}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
